---
title: "My Dazzling Report"
author: "Lindsey Dietz, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: 	
      bg: "#191919"
      fg: "#FDF7F7"
      primary: "#00ffff"
      base_font:
        google: "Prompt"
      code_font:
        google: "JetBrains Mono"
    code_folding: hide
    code_download: true
params:
  dept: 'HR Committee'
  plot_type: 
      value: 'highcharter'
      choices: ['highcharter', 'ggplot2', 'plotly']
  data_start_date: '2005-01-01'
  data_end_date: '2022-03-01'
---
<!-- (stuff above this line is YAML Ain't Markup Language (YAML) and behaves differently than the rest of the doc) -->

<!-- (Setting defaults about your R code chunks) -->
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

<!-- (using parameters in Rmarkdown; don't forget the r) -->
<!-- (This statement above all tabs) -->
This is my report for the `r paste(params$dept)`. I'm creating a plot using `r paste(params$plot_type)`. This text lives "above the fold".  

<!-- (making tabs) -->
<!-- # header 1, all tabs need to be ## header 2 to nest -->

# {.tabset .tabset-pills}

## Some Info

<!-- (** makes it bold) -->
**This is really important information that people should read before looking at my output.**

Here is a key formula that the reader should be aware of:

<!-- (Using LaTeX syntax) -->
$y = \beta_0 + \beta_1 x + \epsilon; 
\epsilon \sim N(0,\sigma^2)$.

References:

<!-- (one type of link) -->
 - How I made the tabs: https://bookdown.org/yihui/rmarkdown-cookbook/html-tabs.html

<!-- (another type of link) -->
 - [Using Rmarkdown in your development process](https://rstudio.com/resources/rstudioconf-2020/rmarkdown-driven-development/)

<!-- (another type of link) -->
These are the R packages I'm going to highlight:

<!-- (R code chunk completely hidden by using include == FALSE) -->
```{r libraries1, include = FALSE}
library(dplyr)
library(tidyr)
```

```{r libraries2, echo = TRUE}
#The report
library(rmarkdown)
#Theming
library(bslib)

#Tables
library(DT)

#Plots
library(ggplot2)
library(plotly)
library(highcharter)
```

I'm getting some unemployment data from FRED to demo.

```{r, results = 'hide', echo = TRUE}
# Source an R script using the relative location
# Made possible because of the R project
source("../scripts/fred_script.R")

# Create a data frame of info for tech analysts
analyst_info <- data.frame(data_start_date = params$data_start_date, 
                           data_end_date = params$data_end_date)

# Run the function from my script using RMD parameter settings
df <- fred_function(start_date = params$data_start_date,
                    end_date = params$data_end_date)
```

<!-- Directly add HTML into a report -->
<details>
<summary> Analysts might want to view this information to confirm the correct data was used. 
</summary>
```{r}
print(analyst_info)
```
</details>

## Interactive Tables {.tabset .tabset-dropdown}
<!-- Try changing .tabset-pills to .tabset-dropdown -->

<!-- Second set of tabs -->
### with DT

[The R package `DT` provides an R interface to the JavaScript library DataTables](https://rstudio.github.io/DT/). R data objects (matrices or data frames) can be displayed as tables on HTML pages, and DataTables provides filtering, pagination, sorting, and many other features in the tables.

<!-- (Generate a table) -->
```{r fred_table}
DT::datatable(df, 
              filter = 'top', 
              extensions = 'Buttons', 
              options = list(dom = 'Bfrtip', 
                             buttons = c('copy', 'csv', 'excel')))
```

## Interactive or Fixed Plot

<!-- (Generate a plot) -->
```{r plot, fig.width=10}

myplot <- ggplot(df, aes(x = Date, y = UR, color = Category)) + 
  geom_line() +
  theme_bw() + 
  ylab("Unemployment Rate")

if(params$plot_type == 'plotly'){
  # Print dynamic plot with plotly 
  ggplotly(myplot)
  
} else if (params$plot_type == 'highcharter'){
  
 # Print dynamic plot with highcharter
 df %>% 
  dplyr::select(Date, Category, UR) %>% 
  highcharter::hchart(., 
         type = "line", 
         hcaes(x = Date, y = UR, group = Category)) %>% 
  hc_yAxis(opposite = TRUE, labels = list(format = "{value}%")) %>% 
  hc_tooltip(pointFormat = '{point.x:%Y-%m-%d}')
  
} else if (params$plot_type == 'ggplot2'){
  # Print fixed ggplot
  myplot
}

```